%====================
% EXPERIENCE A
%====================
\subsection{{Data Analyst \hfill October 2021 --- July 2022}}
\subtext{Food Bank of Contra Costa and Solano \hfill Concord, CA}
\begin{zitemize}
\item Utilized Salesforce reports and SQL to develop donor segmentation models for increasing engagement and other strategic goals.
\item Performed database research to evaluate campaigns and refine cultivation strategies.
\item Build reports and dashboards in Salesforce to make insights accessible and provide recommendations.
\item Documenting processes to clean data, reduce errors, and standardize formatting.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{IT/Technical Support \hfill August 2019 --- November 2019}}
\subtext{Studylog, Inc. \hfill South San Francisco, CA}
\begin{zitemize}
\item Took ownership of rollout of CRM migration, documenting best practices, and implementing integrations and data backup plans.
\item Provided on-premise and remote business customer support.
\item Led weekly support meetings to distribute long term and ad-hoc issues to other team members.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Network Operations and Support Engineer  \hfill September 2014 --- February 2017}}
\subtext{Biscom, Inc. \hfill Chelmsford, CA}
\begin{zitemize}
\item Assisted network and system engineers in integration and configuration of enterprise servers.
\item Worked in NOC utilizing Python and SQL to develop web-based reporting and dashboards, increasing service reliability.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Trading System Analyst \hfill May 2014 --- July 2014}}
\subtext{Boston Technologies Inc. \hfill Boston, MA}
\begin{zitemize}
\item Provided 24/5 Forex, Metals, and Derivative Contracts (CFD) trading support to brokers.
\item Monitored containerized data feed, trade, and liquidity systems.
\item Used SQL to investigate order executions and troubleshoot networks and systems.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{Software Development \hfill July 2013 --- March 2014}}
\subtext{CarrierStore \hfill Maynard, MA}
\begin{zitemize}
\item Used Java, SQL, and JavaScript/jQuery to develop on Salesforce platform.
\item Enforced Test Driven Development and rewrote unite tests to properly test code.
\end{zitemize}
